---
title: "Unit Test Practice"
format: html
editor: visual
---

## Unit testing with the `test that` package

First, intstall necessary pakages

```{r}
#install.packages("testthat")
#install.packages("devtools")
#install.packages("remotes")

library(testthat)
library(devtools)
library(remotes)
```

write a function to practice unit tests.

This function is going to find mean val of each column, and then return the lowest and highest mean value calculated

We would expect:

-   the output to be numeric
-   output should be vector of length 2
-   first value should be smaller than the second value

#will return mean vals

```{r}
mean_range <- function(df)  {
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE) 
col_mean_max <- max(col_means)
col_mean_min <- min(col_means)

return(c(col_mean_min, col_mean_max))
}

mean_range(df = mtcars)
```

Write some unit tests

```{r}
# test that the output is of length
expect_length(mean_range(df = mtcars), 2)

# test that first val is less than second val
expect_true(mean_range(mtcars)[1] < mean_range(mtcars)[2])

if ((mean_range(mtcars)[1] < mean_range(mtcars)[2]) {
  stop()
}
```
```{r}
# source our food cart functions
source(here::here("src", "food_cart_functions.R"))

# Test running function
name_cart(food = "strawberry", animal = "marmot")
```


